Tables/Graphs for Article

### 2018-01-14 article/draft1.Rnw
reformated tables of splines and final model results, changed rounding in table of metrics

@@

\section*{Abstract} % fix the hazard ratios!!!!

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question receives it's first response. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR...), factors related to the question's title (e.g., whether or not it was phrased as a question (HR..)), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR..)). Future studies can investigate whether factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

However, analysis and prediction of response times on CQAs have not been thoroughly investigated. There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality. This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to response time and to predict the survival probability of a question.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions and created a model to predict how long a question would remain unanswered. All research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

@@

% Table of derived predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{2cm} | p{10cm} |}
  \hline
  \multirow{9}{2cm}{Categorical Variables} & Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
  & Whether or not the question's text contains any end punctuation marks (. ? !) \\ \cline{2-2}
  & Whether or not the question's text is in all lower case \\ \cline{2-2}
  & Whether or not the question's title contains at least one word considered to be ``frequently used'' among answered questions \\ \cline{2-2}
  & Whether or not the question's title contains at least one word considered to be ``frequently used'' among unanswered question \\ \cline{2-2}
  & Whether or not the question's title ends in a question mark \\ \cline{2-2}
  & Whether or not the user edited or added information to the question's text after posting it \\ \cline{2-2}
  & Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
  \multirow{5}{2cm}{Continuous Variables} & Average number of characters in each question's tags (Average tag length) \\ \cline{2-2}
  & Average frequency for all of a question's tags. Frequency defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a value of 0 (Average tag frequency) \\ \cline{2-2}
  & Number of characters in the question's text (Text length) \\ \cline{2-2}
  & Number of characters in the user-defined device name (Device name length) \\ \cline{2-2}
  & Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
\end{tabular}
\caption{Categorical and Continuous variables derived}
\label{table:variables}
\end{table}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received. See Appendix for examples of answered and unanswered questions. Variables derived can be found in Table \ref{table:variables}. See Appendix for more details on variable derivation.

@@

Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}. Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}. From these estimates, survival curves were constructed to examine the survival experience of questions. Mean, median and other percentiles of survival times were also generated.

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univariate Cox models and strength of association with response times was assessed. Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.  Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with transformations and splines found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than including all predictors.

@@

% % Univariate analysis results
% \begin{table}[!htbp]
% \centering
% \begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
%   \hline
%   \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
%   \hline \hline
%   \multirow{ 3 }{ 5cm }{ Average tag frequency }
%   & Untransformed & 1.270620e-08 \\
%   & Log + 1 & 1.186521e-08 \\
%   & \textbf{*}Square root & 1.464184e-11 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Average tag length }
%   & Untransformed & 2.611529e-02 \\ 
%   & \textbf{*}Log + 1 & 6.018542e-05 \\
%   & Square root & 2.999917e-04 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Device name length }
%   & Untransformed & 6.530431e-03 \\
%   & \textbf{*}Log + 1 & 1.912977e-05 \\
%   & Square root & 2.291424e-04 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
%   & Untransformed & 1.398819e-07 \\
%   & Log + 1 & 1.092952e-07 \\
%   & \textbf{*}Square root & 1.148792e-11 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Text length }
%   & Untransformed & 6.947221e-12 \\
%   & \textbf{*}Log & 0.000000e+00 \\
%   & Square root & 1.110223e-16 \\ \hline \hline
%   \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
%   \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
% \end{tabular}
% \caption{Univariate analysis results} 
% \label{table:univariate_results}
% \end{table}

@@

train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
@

Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions, and each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions. Univariate analysis performed on one training set indicated that all cateogorical predictors were signficant with partial likelihood ratio p-values of less than 0.001. All continuous predictors, except for device length and average tag length, also resulted in univariate p-values of less than 0.001. Applying either square root or log transformations to continuous variables resulted in univariate p-values of less than 0.001. For continuous predictors that contained zeros, one was added to each observation before applying the log transformation. The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length. All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.

% Splines
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
  \hline
  \multirow{ 4 }{ 5cm }{ Log transformation of text length } 
  & 0 & 65862.83 \\ 
  & \textbf{*}5 & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of line breaks to text length ratio }
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & \textbf{*}3 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average tag frequency }
  & \textbf{*}0 & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of device name length + 1 }
  & 0 & 65918.06 \\ 
  & \textbf{*}5 & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of average tag length + 1 }
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & \textbf{*}4 & 65910.81 \\ 
  & 3 & 65914.98 \\ 
   \hline
\end{tabular}
\caption{Determining the optimal k number of splines for each predictor} 
\label{table:splines}
\end{table}

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.027030 & 937.3877 & 0.0000 & 0.1401511 & 0.2683734 & 0.6341867 \\ 
  \textbf{Test Sets} & 1.986844 & 220.8309 & 0.0000 & 0.1400518 & 0.2582790 & 0.6291395 \\
  \textbf{Full Data} & 2.028051 & 1165.0321 & 0.0000 & 0.1394092 & 0.2672884 & 0.6336442 \\ 
   \hline
\end{tabular}
\caption{Performance Metrics. HR: Hazard Ratio, LR: Partial Likelihood Ratio} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{3cm} p{4cm}| c | c |}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  \multirow{ 9 }{ 3 cm }{ Device Category } & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
  & Camera & -0.3199 (0.0476) & \\ 
  & Electronics & -0.0138 (0.0904)  & \\ 
  & Game Console & 0.2458 (0.0784)  & \\ 
  & Home & 0.3368 (0.0697) &  \\ 
  & Other & -0.1304 (0.0555)  & \\ 
  & PC & 0.2818 (0.0597) &  \\ 
  & Tablet & -0.1566 (0.0815)  & \\ 
  & Vehicle & 0.4056 (0.0695)  & \\ 
  \hline
  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & -0.1334 (0.0331)  & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & 0.6127 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) &  0.0060 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) &  0.2596 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & -0.2808 (0.0340)  & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) &  <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857)  & 0.0005 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364)  & 0.0031 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362)  & 0.0448 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average tag frequency } & 2.2609 (0.7196)  & 0.0020 \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model.Continous predictors with restricted cubic splines are not shown. } 
\label{table:coefficients}
\end{table}

@@

The following are interpretations of select hazard coefficients in Table \ref{table:coefficients}. Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not received an answer by that time.

@@

The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design. Many users asking a question incorrectly specified the device name (e.g. A user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic). It is likely that these inconsistencies contributed to the final model's low predictive power. This, along with the results of the final model, reveal some of the ways that the CQA can be structured to improve analysis and decrease response time. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions. Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above. Instead, the CQA can restrict the tags or devices that users can include to a drop-down list. The CQA can also include more tips to guide users asking questions. Establishing and implementing a more restrictive framework for asking questions can help users ask understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.

@@

\section*{7. Acknowledgement}

@@

\subsubsection*{8.2.1 Device Categorization}

@@

\subsubsection*{8.2.2 Whether or not the question's text contained at least one end punctuation mark}

@@

\subsubsection*{8.2.3 Whether or not the question's title contains terms considered to by frequently-used among answered/unanswered questions}

@@

% Table with list of frequently used words
\begin{table}[!htbp]
\centering
\begin{tabular}{|L{4cm}|p{8cm}|}
  \hline
 \textbf{Frequently-used terms among answered questions} & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
  \hline
  \textbf{Frequently-used terms among unanswered questions} & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\ 
   \hline
\end{tabular}
\caption{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
\label{table:frequent_terms}
\end{table}

@@

\subsubsection*{8.2.4 Whether or not the question's title ended in a question mark}

@@

\subsubsection*{8.2.5 Whether or not the user made an effort to solve the problem on their own, prior to asking the question}

@@

\subsubsection*{8.2.6 Average tag frequency}

This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times. This variable is the average frequency, or proportion of times a question's tags appear in all of the data set. If a question has a higher average, than at least one of it's tags are frequently used. This variable was created based off of findings from \cite{Bhat2014}.

\subsubsection*{8.2.7 Average tag length}

\subsubsection*{8.2.8 Device name length}

\subsubsection*{8.2.9 Line break to text length ratio}

>>>>

\usepackage{caption}

@@

\section*{Abstract}

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question receives it's first response. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

However, analysis and prediction of response times on CQAs have not been thoroughly investigated. There is need for further analysis of forum response times, as the majority of existing research focuses on assessing and predicting question or answer quality. This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to response time and to predict survival probabilities of questions.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions and created a model to predict how long a question would remain unanswered. Howerver, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

@@

% Table of derived predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{| L{2cm} | L{10cm} |}
  \hline
  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
  & If the question's text is in all lower case \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
  & If the question's title ends in a question mark \\ \cline{2-2}
  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
  & If the user made an effort to solve the problem prior to asking the question \\ \hline
  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (Average tag length) \\ \cline{2-2}
  & Average frequency for all of a question's tags. Frequency defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a value of 0 (Average tag frequency) \\ \cline{2-2}
  & Number of characters in the question's text (Text length) \\ \cline{2-2}
  & Number of characters in the user-defined device name (Device name length) \\ \cline{2-2}
  & Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
\end{tabular}
\caption{Categorical and continuous variables derived}
\label{table:variables}
\end{table}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download). Variables in the data included: device name and category, title, text, tags, If the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received. See Appendix for an example of an answered and unanswered question. Variables derived can be found in Table \ref{table:variables}. See Appendix for details on variable derivation.

@@

Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}. Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}. From these estimates, survival curves were constructed to examine the survival experience of questions. Mean and median survival times were also generated.

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univariate Cox models and strength of association with response times was assessed. Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.  Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with transformations and splines found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than retaining all predictors.

@@

@@

train1 <- x[splitPlan[[1]]$train, ]
test1 <- x[splitPlan[[1]]$app, ]
@

Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions. Each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions. Univariate analysis performed on one training set indicated that all categorical predictors were signficant with partial likelihood ratio p-values of less than 0.001. Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001. Applying either square root or log transformations resulted in univariate p-values of less than 0.001. For those that contained zeros, one was added to each observation before applying the log transformation. The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length. All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.

% Splines
\begin{table}[!htbp]
\centering
\begin{tabular}{| L{5cm} | l | l |}
  \hline
  \textbf{Predictor} & \textbf{K} & \textbf{AIC} \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of the average tag frequency }
  & \textbf{*}0 & 65890.75 \\ 
  & 5 & 65891.69 \\ 
  & 4 & 65891.75 \\ 
  & 3 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of average tag length + 1 }
  & 0 & 65920.24 \\ 
  & 5 & 65911.20 \\ 
  & \textbf{*}4 & 65910.81 \\ 
  & 3 & 65914.98 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Log transformation of device name length + 1 }
  & 0 & 65918.06 \\ 
  & \textbf{*}5 & 65847.34 \\ 
  & 4 & 65880.89 \\ 
  & 3 & 65898.00 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{ Square root transformation of line breaks to text length ratio }
  & 0 & 65890.28 \\ 
  & 5 & 65884.70 \\ 
  & 4 & 65882.98 \\ 
  & \textbf{*}3 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5cm }{ Log transformation of text length } 
  & 0 & 65862.83 \\ 
  & \textbf{*}5 & 65862.02 \\ 
  & 4 & 65863.35 \\ 
  & 3 & 65862.08 \\ 
  \hline
\end{tabular}
\caption{Determining the optimal k number of splines for each continuous predictor} 
\label{table:splines}
\end{table}

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.03 & 937.39 & 0 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test Sets} & 1.99 & 220.83 & 0 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full Data} & 2.03 & 1165.03 & 0 & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}
\caption{Performance Metrics. \\ HR: Hazard Ratio, LR: Partial Likelihood Ratio} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|l L{4cm}| c | c |}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
                  & Camera & -0.3199 (0.0476) & \\ 
                  & Electronics & -0.0138 (0.0904)  & \\ 
                  & Game Console & 0.2458 (0.0784)  & \\ 
                  & Home & 0.3368 (0.0697) &  \\ 
                  & Other & -0.1304 (0.0555)  & \\ 
                  & PC & 0.2818 (0.0597) &  \\ 
                  & Tablet & -0.1566 (0.0815)  & \\ 
                  & Vehicle & 0.4056 (0.0695)  & \\ \hline
  \multicolumn{2}{|l|}{Weekend or weekday} & -0.1334 (0.0331)  & <0.0001 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's text contains end punctuation marks} & 0.0247 (0.0499) & 0.6127 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the question's title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the user edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the user had been a member for less than one day before posting the question} & -0.1069 (0.0364)  & 0.0031 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{If the user made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
  \multicolumn{2}{|L{7.5cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model. Continous predictors fit with restricted cubic splines are not shown.} 
\label{table:coefficients}
\end{table}

@@

The following are interpretations of select hazard coefficients in Table \ref{table:coefficients}. Hazard is approximately equivalent to the conditional probability that a question will receive an answer within the next moment in time, given that it has not already received an answer.

@@

The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design. Many users incorrectly specified the device name (e.g. A user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic). It is likely that these inconsistencies contributed to the final model's low predictive power. This, along with the results of the final model, reveal some of the ways that the CQA can be structured to improve analysis and decrease response time. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions. Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above. Instead, the CQA can restrict the tags or devices that users can include to a drop-down list. The CQA can also include more tips to guide users asking questions. Implementing a more restrictive framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.

@@

\section*{7. Acknowledgements}

@@

\subsubsection*{8.2.1 Average tag frequency}

This variable was created to investigate if including popular or widely-used tags in a question lead to faster response times. This variable is the average frequency, or proportion of times a question's tags appear in all of the data set. If a question has a higher average, than at least one of its tags are considered frequently-used. This variable was created based off of findings from \cite{Bhat2014}.

\subsubsection*{8.2.2 Average tag length}

\subsubsection*{8.2.3 Device Categorization}

@@

\subsubsection*{8.2.4 Device name length}

\subsubsection*{8.2.6 If the question's text contains end punctuation marks}

@@

\subsubsection*{8.2.7 If the question's title contains terms considered frequently-used among answered/unanswered questions}

@@

% Table with list of frequently-used words
\begin{table}[!htbp]
\centering
\begin{tabular}{|L{4cm}|L{8cm}|}
  \hline
 \textbf{Frequently-used terms among answered questions} & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
  \hline
  \textbf{Frequently-used terms among unanswered questions} & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\ 
   \hline
\end{tabular}
\caption{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
\label{table:frequent_terms}
\end{table}

@@

\subsubsection*{8.2.8 If the question's title ends in a question mark}

@@

\subsubsection*{8.2.9 If the user made an effort to solve the problem prior to asking the question}

@@

\subsubsection*{8.2.5 Line break to text length ratio}
